Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2021-01-30 paper/paper.tex
paper: Rearrange pictures

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../figures/melotte_22/features_melotte_22.png}
  \caption{Pairwise relationships among variables using Melotte 22 data}
  \label{fig:features_melotte_22}
\end{figure}

@@

@@

\begin{figure}
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \begin{subfigure}[t]{0.3\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/kmeans/kmeans_n2_pm_melotte_22.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.3\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/kmeans/kmeans_n5_pm_melotte_22.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.3\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/kmeans/kmeans_n8_pm_melotte_22.png}
    \end{subfigure}
  \end{subfigure}
  \medskip
  \begin{subfigure}{\columnwidth}
    \centering
    \begin{subfigure}[t]{0.3\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/kmeans/kmeans_n2_parallax_melotte_22.png}
      \caption{N = 2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.3\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/kmeans/kmeans_n5_parallax_melotte_22.png}
      \caption{N = 5}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.3\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/kmeans/kmeans_n8_parallax_melotte_22.png}
      \caption{N = 8}
    \end{subfigure}
  \end{subfigure}
  \caption{K-Means comparisons with Melotte 22}
  \label{fig:kmeans_comparisons_melotte_22}
\end{figure}

@@

All developed resources are available at:
\href{github.com/cdalvaro/machine-learning-master-thesis}{github.com/cdalvaro/machine-learning-master-thesis}

>>>>

\begin{figure}[htbp]
  \includegraphics[width=\columnwidth]{../figures/melotte_22/features_melotte_22.png}
  \caption{Pairwise relationships among variables using Melotte 22 data}
  \label{fig:features_melotte_22}
\end{figure}

@@

@@

\begin{figure}[htbp]
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \begin{subfigure}[t]{0.3\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/kmeans/kmeans_n2_pm_melotte_22.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.3\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/kmeans/kmeans_n5_pm_melotte_22.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.3\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/kmeans/kmeans_n8_pm_melotte_22.png}
    \end{subfigure}
  \end{subfigure}
  \medskip
  \begin{subfigure}{\columnwidth}
    \centering
    \begin{subfigure}[t]{0.3\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/kmeans/kmeans_n2_parallax_melotte_22.png}
      \caption{N = 2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.3\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/kmeans/kmeans_n5_parallax_melotte_22.png}
      \caption{N = 5}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.3\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/kmeans/kmeans_n8_parallax_melotte_22.png}
      \caption{N = 8}
    \end{subfigure}
  \end{subfigure}
  \caption{K-Means comparisons with Melotte 22}
  \label{fig:kmeans_comparisons_melotte_22}
\end{figure}

@@

@@

All resources developed for this project are available at the GitHub repository:
\href{https://github.com/cdalvaro/machine-learning-master-thesis}{cdalvaro/machine-learning-master-thesis}

It includes the DEC model developed in Python using the Keras framework
and Jupyter Notebooks \cite{Kluyver2016jupyter} with examples.
